%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Ales Guzik} % Your name
\address{Lopatina st. 3-89 \\ Minsk, Belarus 220125} % Your address
\address{+375~29~575-1103 \\ me@aguzik.net} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Belarusian State University of Informatics and Radioelectronics, Minsk} \hfill {\em July 2013} \\ 
Faculty of Computer Systems and Networks \\
M.S. in Computer Science \& Software Engineering \smallskip \\
{\bf Belarusian State University of Informatics and Radioelectronics, Minsk} \hfill {\em July 2012} \\ 
Faculty of Computer Systems and Networks \\
B.S. in Systems Engineering \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNOLOGY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Have experience with}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Operating Systems     & Linux (Arch, Debian, CentOS, Ubuntu), Mac OS X \smallskip \\
Programming Languages & Clojure, Ruby, C, Bourne-compatible shells, JavaScript, Perl, C++, \\
                      & Common Lisp, Erlang, Factor, Scheme, Lua, Python and more\smallskip \\
Markup and Typesetting & \LaTeX, HTML, HAML, Slim, CSS, SASS/SCSS, Less, \\
                       & Twitter Bootstrap \smallskip \\
Server technologies   & Chef, Nginx, Apache httpd, OpenSSH, Postfix, Prosody, vsftpd,\\
                      & Squid, Corosync, Pacemaker, DRBD, \smallskip \\
SQL Databases & PostgreSQL, MySQL/MariaDB, SQLite \smallskip \\
NoSQL Databases & Neo4j, OrientDB, MongoDB, Cassandra \smallskip \\
Tools & zsh, git, emacs, vim, tmux, gpicker, ctags, the silver searcher, \\
      & GNU Global, splint, gdb, strace, valgrind, gprof \smallskip \\
Programming paradigms & Imperative, Object-oriented (class-based, prototype-based), \\
                      & Functional, Concatenative (stack-based).
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	NOTES SECTION
%----------------------------------------------------------------------------------------

%% \begin{rSection}{Spheres of interest}
%%   \smallskip
%%   \begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
%%     \itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
%%   \item Programming languages
%%   \item Productivity in software development
%%   \end{list}
%% \end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work positions}

\begin{rSubsection}{Rubyroid Labs, LLC}{April 2014 - Present}{Senior Software Engineer}{Minsk, Belarus}
~
\end{rSubsection}

\begin{rSubsection}{Intetics Co.}{July 2013 - April 2014}{Senior Software Engineer}{Minsk, Belarus}
\item Made fully-automated production server setup
\item Worked on refactoring legacy codebase
\item Worked on security-related features (ip whitelisting, xss testing)
\item Implemented backend service for mobile apps.
\item Implemented automatic management of VPN servers DNS rotation
\end{rSubsection}

\begin{rSubsection}{\parbox[t][2em][t]{9cm}{Belarusian State University of Informatics and Radioelectronics}}{February 2013 - January 2014 }{Teaching assistant at Electronic Computing Machines Department (part-time)}{Minsk, Belarus}
\item Taught students how to use git and github.
\item Together with students formalized grading criteria.
\item Formalized some code quality metrics.
\item Taught interested students linux in my spare time.
\end{rSubsection}

\begin{rSubsection}{PowerMeMobile, Inc.}{January 2013 - February 2013}{Problem solver}{Minsk, Belarus}
\item Gave an idea of automating deployment process (new tier deployments may take up to
  a month of SysAdmin team work).
\item Implemented initial stages of deployment automation (installing base cluster software,
  configuring corosync/pacemaker, installing and configuring DRBD and nginx as resource agents) using Chef.
\item Made entire deployment configurable from a single place (from chef workstation using node attributes).
\item Got an agreement on opensourcing this efforts.
\end{rSubsection}

\begin{rSubsection}{Altoros Systems, Inc.}{October 2011 - September 2012}{Software Engineer in Ruby department}{Minsk, Belarus}
\item Proved that custom multisite functionality is a bad idea. Dropped the hacks and refactored application to use rails 3 engines.
\item Participated in porting internal RightScale services (mostly sinatra+cassandra) to JRuby to utilize native Thrift.
\item Participated in all stages of design and development on many projects.
\end{rSubsection}

\begin{rSubsection}{Itransition, Inc.}{February 2011 - October 2011}{Junior Developer in Ruby department}{Minsk, Belarus}
\item Solely ported large social gaming engine from Rails 2 to Rails 3.
\item Initiated using SCSS and Compass, which led to stylesheets development and modification speedup.
\item Configured production server from scratch and setup automated Capistrano deployment.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	NOTES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Some random facts}
  \smallskip
  \begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
    \itemsep -0.5em \vspace{-0.5em} % Compress items in list together for aesthetics
  \item I use Dvorak keyboard layout
  \item I like cycling
  \item First time I installed and started playing with linux was 9 years ago (it was
    Mandrake 10 in 2005)
  %% \item This summer I took part in ``System administrator 2012'' (http://admin2012.ru)
  %%   contest and surprisingly received ``Guru'' certificate (top 4.1\%)
  \item Somewhere in the past I was passionate about japanese animation, so I learned
    some japanese (have JLPT4 certificate)
  \item I have contributed to upstream of at least 11 opensource project
      and have some personal opensource projects.
  \item I am in an eternal search for a perfectly expressive programming language.
  \end{list}
\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
